Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-07 implementation.tex

The view computation renders the model (i.e. a Z-expression paired with a type) as nested HTML \texttt{div} elements matching the tree structure of the corresponding Z-expression. This tree is stylized separately using CSS. The action palette is a collection of buttons and text boxes which
are disabled when the corresponding action cannot be performed. We determine this by simply attempting to perform the
action internally and handling the exception that is raised when an action
is undefined. Each action form also has a corresponding keyboard shortcut. This design is not, of course, meant to score marks for
usability or performance. Instead, as a simple reference implementation, it allows the reader to interact with the concepts presented in this paper, to aid in their understanding.  Additionally, we expect its source code to be of use to others who are interested in
layering a more fluid user interface atop the core semantics, or extensions thereof.

>>>>

The view computation renders the model (i.e. a Z-expression paired with a type) as nested HTML \texttt{div} elements matching the tree structure of the corresponding Z-expression. This tree is stylized separately using CSS. The action palette is a collection of buttons and text boxes which
are disabled when the corresponding action cannot be performed. We determine this by simply attempting to perform the
action internally and handling the exception that is raised when an action
is undefined. Each action form also has a corresponding keyboard shortcut. This design is not, of course, meant to score marks for
usability or performance. Instead, as a simple reference implementation, it allows the reader to interact with the system presented in this paper, to aid in their understanding.  Additionally, we expect its source code to be of use to others who are interested in
layering a more fluid user interface atop the core semantics, or extensions thereof.
